---
title: "Online Retail Data Analysis"
subtitle: "Sales, Customer, Product, Country and Cancellation Insights"
author: "Johnson Acharya"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    code-fold: true
    code-tools: true
    embed-resources: true
    fig-width: 10
    fig-height: 6
    theme: cosmo
execute:
  echo: false
  warning: false
  message: false
---

# Executive Summary

This report analyzes online retail transaction data to identify key sales, customer, product, geographic and cancellation trends.

The analysis focuses on understanding overall business performance, identifying high-performing products and customers, evaluating geographic patterns, and understanding cancellation activity.

# Introduction

## Business Context

Online retail businesses generate large volumes of transactional data that can be used to understand purchasing behavior, revenue patterns, product performance and customer activity.

This analysis uses historical online retail transaction data to explore these business questions.

## Objectives

The main objectives of this analysis are to:

-   Understand overall sales performance
-   Identify monthly and seasonal sales patterns
-   Identify high-value customers
-   Identify high-performing products
-   Compare country-level performance
-   Analyze order cancellations
-   Generate actionable business recommendations

## Analysis Areas

The analysis covers the following areas:

-   Sales Overview
-   Time Analysis
-   Customer Analysis
-   Product Analysis
-   Country Analysis
-   Cancellation Analysis

## Data Source

The analysis is based on the Online Retail transactional dataset.

The raw dataset is stored in:

`data/raw/Online_Retail.xlsx`

The analysis pipeline transforms the raw data into cleaned and feature-engineered datasets before the business analysis is performed.


# Sales Performance

## Overview

This section evaluates the overall sales performance of the online
retail business using revenue, order and customer-level metrics.

The analysis focuses on understanding the scale of the business and
identifying the overall sales trend across the available period.

### Overall Sales KPIs

```{r}
sales_overview <- readr::read_csv(
  "../outputs/tables/sales_overview.csv",
  show_col_types = FALSE
)

knitr::kable(
  sales_overview,
  digits = 2,
  caption = "Overall Sales Performance"
)
```

### Annual Sales Performance

Annual sales performance provides a high-level view of how revenue
changed across the available years.

```{r}
annual_sales <- readr::read_csv(
  "../outputs/tables/annual_sales.csv",
  show_col_types = FALSE
)

knitr::kable(
  annual_sales,
  digits = 2,
  caption = "Annual Sales Performance"
)
```

### Monthly Revenue Trend

Monthly revenue helps identify periods of higher and lower sales
activity and provides insight into the seasonal pattern of the
business.

```{r}
knitr::include_graphics(
  "../outputs/plots/monthly_revenue.png"
)
```

### Interpretation

Monthly revenue varies across the year, with some months showing stronger sales than others. The lowest revenue was recorded in February 2011 at approximately 523,000, while revenue increased during several months that followed.

Sales were particularly strong from September to November 2011, with revenue reaching its highest level in November at approximately 1.50 million. Overall, the chart suggests that the business experienced stronger sales activity toward the later months of 2011